Contextuality and Nonlocality in Discrete Quantum Theory

### 2015-11-26 DQC3.tex
Keep editing comments on "The Concept of Contextuality and its..."

\yutsung{Does the sentences in this paragraph contradict to each
other? I think Peres~\cite{peres1995quantum} means: If we think
the measurement process as a quantum system by the Born rule, the
measurement result does not depend on simultaneously measuring commuting
observables. On the other hand, if we want to think the measurement
process classically, i.e., to assign the measurement result for each
observable, we cannot make the assignment prior to any measurement,
and assume that measuring commuting observables does not change the
assigned measurement result. <- This long sentence means contextuality.}

>>>>

\yutsung{Does the sentences in this paragraph contradict to each
other? According to the postulates in page 206 and 207 in Peres~\cite{peres1995quantum},
this paragraph should read ``Quantum Physics is contextual, meaning
that if we predetermine definite outcomes for any measurement, then
the predetermined outcomes depend not only on the choice of the measured
observable(s) and on the system being measured, but also on the details
of the measurement process. To be more precise, as noted by Peres~\cite{peres1995quantum}
and Mermin~\cite{MerminPRL1990}, the result of measuring an observable
in a physical system must not depend on whether we measure the observable
alone, or along with arbitrary sets of mutually commuting observables.
However, if we try to predetermine definite measurement outcomes for
all observables on a system, the predetermined outcome of an observable
$\mathbf{O}$ will be changed by measuring other observables commuting
to $\mathbf{O}$.''}

\yutsung{Personal note about the reason why the quantum physics is
contextuality, and a bit of literature review. Don't know whether
or where to put them in our paper through.

In order to prove by contradiction, assume the quantum physics is
non-contextuality, i.e., 
\begin{enumerate}
\item \label{enu:non-contextuality}Given an observable $\mathbf{O}$, the
predetermined definite outcome $v\left(\mathbf{O}\right)$ does not
depend on the choice of compatible observables that may be preformed
together with it. (postulate I in page 207 in \cite{peres1995quantum}).
\end{enumerate}
This leads to the premise of the Kochen-Specker theorem
\begin{enumerate}[resume]
\item \label{enu:premise}For a set of commuting projection operator $\proj{n}$,
if $\left\{ \ket{n}\right\} $ forms a basis, then $\sum_{n}v\left(\proj{n}\right)=1$.
(page 196 in \cite{peres1995quantum}).
\end{enumerate}
The Kochen-Specker theorem says Premise (\ref{enu:premise}) is impossible
to be satisfied so that postulate (\ref{enu:non-contextuality}) fails,
and the quantum theory is contextual .

Schumacher and Westmoreland~\cite{2010arXiv1010.5452S} uses Premise
(\ref{enu:premise}) instead of Postulate (\ref{enu:non-contextuality})
as the definition of non-contextuality because lack of commuting observables
in their theory. Our paper can do better and use Assumption (\ref{enu:non-contextuality})
as non-contextuality.

There is no solid reason why people assume Postulate (\ref{enu:non-contextuality})
as a postulate. Peres gives a ``psychological reason'' that Postulate
(\ref{enu:non-contextuality}) is true when the measurement outcome
is predictable. Another ``psychological reason'' might be: because
Postulate (\ref{enu:non-contextuality}) is true when we replace the
``predetermined definite outcome'' by the usual ``measurement result''
in CQT. However, in DQT, because commuting observables cannot be measured
simultaneously, it may not be surprising that Postulate (\ref{enu:non-contextuality})
is false.}
